Variance reduction for MCMC methods via martingale representations

### 2020-01-23 aap/Revision/vr-mcmc-revision.tex
update

Upon estimating  the coefficients \((\widehat a_{l,k})\), one can construct an empirical estimate  of \(M_{K,n}^N(f)\) in the form
\begin{eqnarray*}
\widehat M_{K,n}^N(f) =\sum_{1\leq  k \le K}\sum_{l=N+1}^{N+n}\widehat a_{l,k}(X_{l-1})\phi_k(\xi_{l}).
\end{eqnarray*}
Obviously \(\mathsf{E}[\widehat M_{K,n}^N(f)|\TrainSet]=0\) and \(\widehat M_{K,n}^N(f)\) is indeed a valid control variate in that it
does not introduce any bias.

>>>>

Upon estimating  the coefficients \((\widehat a_{l,k})\), one can construct an empirical estimate  of \(M_{K,n}^N(f)\) in the form
\begin{eqnarray*}
\widehat M_{K,n}^N(f) =\sum_{1\leq  k \le K}\sum_{l=N+1}^{N+n}\widehat a_{l,k}(X_{l-1})\phi_k(\xi_{l}).
\end{eqnarray*}
Obviously \(\mathsf{E}[\widehat M_{K,n}^N(f)|\TrainSet]=0\) and \(\widehat M_{K,n}^N(f)\) is indeed a valid control variate in a sense that it
does not introduce any bias.
